UKB Simulation Analyses

### 2023-12-20 paper_results.Rmd
reworking and updating so that more heavy computation (ie centile error calcs) happen on cubic

Little plots
```{r}
#define plotting functions
plot.cent.diffs <- function(df){
mean.diffs.long <- df %>%
  mutate(dataset = factor(dataset, levels = c("raw", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE)) %>%
  group_by(dataset) %>%
  dplyr::summarize(across(starts_with("abs.diff_"), mean)) %>%
  ungroup() %>%
  dplyr::select(-ends_with(".z")) %>% #drop z-score cols
  pivot_longer(cols=starts_with("abs.diff_"), values_to="centile_abs.diff", names_to = "pheno", names_prefix = "abs.diff_") %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)),
      label = sub("_[^_]*_", "_", pheno))

>>>>

Little plots
```{r}
#define plotting
plot.cent.diffs <- function(df){
mean.diffs.long <- df %>%
  mutate(dataset = factor(dataset, levels = c("raw", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE)) %>%
  group_by(dataset) %>%
  dplyr::summarize(across(starts_with("abs.diff_"), mean)) %>%
  ungroup() %>%
  dplyr::select(-ends_with(".z")) %>% #drop z-score cols
  pivot_longer(cols=starts_with("abs.diff_"), values_to="centile_abs.diff", names_to = "pheno", names_prefix = "abs.diff_") %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)),
      label = sub("_[^_]*_", "_", pheno))

### 2023-12-20 ukb_sim.site_analyses.Rmd
reworking and updating so that more heavy computation (ie centile error calcs) happen on cubic

>>>>

## Varying M:F

pulled centile/z error calcs from cubic using `scp -r 'gardnerm@cubic-login.uphs.upenn.edu:/cbica/home/gardnerm/combat-biovar/ukb_ratios/perm_centile_csvs/*_diffs.csv' .`

pulled within-subj summaries from cubic using `scp -r 'gardnerm@cubic-login.uphs.upenn.edu:/cbica/home/gardnerm/combat-biovar/ukb_ratios/perm_centile_csvs/subject-wise/*.csv' .`

Visualize simulated sites

```{r}
ratio_data_path <- "/Users/megardn/Desktop/BGD_Repos/combat_biovar/derivatives/ukb_ratio"
raw_files <- list.files(path = ratio_data_path, pattern = "_pred.csv", full.names = TRUE)

df <- data.frame() #new empty dataframe
for (file in raw_files) {
  # Read each CSV file
    data <- fread(file)

    # Add a "Source_File" column with the file name
    data <- data %>%
      mutate(Source_File = as.factor(basename(file))) %>%
      mutate(dataset = gsub("_data|_raw.csv|prop-|[0-9]|-", "", Source_File))

    # Bind the data to the combined dataframe
    df <- bind_rows(df, data)
    assign("ratio_sites", df)
}
length(unique(ratio_sites$Source_File))
```

```{r}
ggplot(ratio_sites) +
  geom_bar(aes(x=sim.site, fill=sex), position = "fill") +
  scale_y_continuous(name = "percent",
                     breaks = seq(0, 1, by=0.1), 
                     labels = scales::percent(seq(0, 1, by=0.1))) +
  facet_wrap(~Source_File)
```

```{r}
ggplot(ratio_sites) +
  geom_histogram(aes(x=age_days, fill=sim.site), position = "identity", alpha=0.4, binwidth = 365) +
  facet_wrap(~Source_File)

ggplot(ratio_sites) +
  geom_histogram(aes(x=age_days, fill=Source_File, color=Source_File), position = "identity", alpha=0.4, binwidth = 365)
```

### Centiles
